Local Spectral Clustering of Density Upper Level Sets

### 2019-05-24 neurips/local_spectral_density_clustering_arxiv.tex
Added arxiv version

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2019}

@@

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

There are an almost limitless number of ways to define what the ``right''
clustering is. In this paper, we have considered one such notion---density upper
level sets---and have detailed a set of natural geometric criteria which, when 
appropriately satisfied, translate to provable bounds on estimation of the
cluster by PPR. We do not, however, provide theory to show that our geometric
conditions are required for successful recovery of a density level set. This
seems to be supported by our empirical work, and it remains a direction for
future work.

\clearpage

>>>>

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
     \usepackage[preprint]{neurips_2019}

@@

\author{
Alden Green \And
Sivaraman Balakrishnan \And
Ryan J. Tibshirani}

@@

There are an almost limitless number of ways to define what the ``right''
clustering is. In this paper, we have considered one such notion---density upper
level sets---and have detailed a set of natural geometric criteria which, when 
appropriately satisfied, translate to provable bounds on estimation of the
cluster by PPR. We do not, however, provide theory to show that our geometric
conditions are required for successful recovery of a density level set. This
seems to be supported by our empirical results, and it remains a direction for 
future work.

\clearpage
\appendix
